\documentclass[a4paper, 12pt]{article}

\usepackage{url}
\usepackage{parskip}

\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

\usepackage{tabularx}

\usepackage{enumitem}

\newcolumntype{C}{>{\centering\arraybackslash}X}

\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\usepackage[style=authoryear, sorting=ynt, maxbibnames=10]{biblatex}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks, breaklinks, urlcolor=linkcolour, linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength{\bibitemsep}{1em}

\usepackage{fontawesome5}

\newenvironment{jobshort}[2]{
\begin{tabularx}
	{\linewidth}{@{}l X r@{}} \textbf{#1} & \hfill & #2 \\[3.75pt]
\end{tabularx}
}{ }

\newenvironment{joblong}[2]{
\begin{tabularx}
	{\linewidth}{@{}l X r@{}} \textbf{#1} & \hfill & #2 \\[3.75pt]
\end{tabularx}
\begin{minipage}[t]{\linewidth} \begin{itemize}[nosep,after=\strut, leftmargin=1em,
itemsep=3pt,label=\textbullet] }{ \end{itemize} \end{minipage} }

\begin{document}

\pagestyle{plain}

\begin{tabularx}{\linewidth}{@{} C @{}}
    	\Huge{Md. Mosfikur Rahman} \\[7.5pt]
	\href{https://github.com/mdmosfikurrahman}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \            
	\href{https://linkedin.com/in/mdmosfikurrahman}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \   
	\href{https://mdmosfikurrahman.github.io}{\raisebox{-0.05\height}\faGlobe \ Portfolio} \ $|$ \          
	\href{mailto:mdmosfikurrahman.cse@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ mdmosfikurrahman.cse@gmail.com} \ $|$ \ 
    	\href{tel:+8801332512922}{\raisebox{-0.05\height}\faMobile \ +8801332512922}   \\
\end{tabularx}


\section{\textbf{Career Objective}}
	I am a research-driven software engineer who has been intensively trained in contributing
	towards related research in the fields of Data Science, Machine Learning, and Artificial
	Intelligence using Java. I would be grateful to be involved in research into
	which technological blends would be appropriate for practical application in
	solving real-world problems. I would like to leverage my work experiences in the
	scalable application development area and algorithm design in order to collaborate
	with famous academics and professionals for progressive research and influential
	publications at academic levels that have a contribution toward technological advancement.
	My objective is to utilize my technical expertise along with interest in
	research to make an valued contribution at an academic level by solving
	complex problems using interdisciplinary approaches.

	\section{\textbf{Education}}
	\begin{tabularx}
		{\linewidth}{@{}l X@{}} 2021 & Bachelor of Science (B.Sc.) in Computer Science
		and Engineering
		\newline
		\textbf{Daffodil International University, Bangladesh} \hfill (CGPA: 3.83/4.00)
		\\

		2021 & Exchange Program in Computer Science and Engineering
		\newline
		\textbf{Adam Mickiewicz University, Poland} \hfill (Passed with 80\% Marks)
		\\

		2016 & Higher Secondary School Certificate
		\newline
		\textbf{Major General Mahmudul Hasan Adarsha College, Tangail} \hfill (GPA:
		4.67/5.00) \\

		2014 & Secondary School Certificate
		\newline
		\textbf{Police Lines Adarsha High School, Tangail} \hfill (GPA: 5.00/5.00)
		\\
	\end{tabularx}

	\section{\textbf{Research Interest}}

	\begin{itemize}[leftmargin=*,itemsep=2pt,parsep=0pt]
		\item Data Science

		\item Machine Learning

		\item Artificial Intelligence

		\item Internet of Things

		\item Software Development
	\end{itemize}

	\section{\textbf{Publications}}
	\begin{refsection}
		[citations.bib] \nocite{*}
		\printbibliography
		[heading=none]
	\end{refsection}

	\section{\textbf{Research Collaborations}}

	\begin{itemize}[leftmargin=*,itemsep=2pt,parsep=0pt]
		\item \textbf{Elsevier Reviewer}, Current Research in Behavioral Science.

		\item \textbf{Elsevier Reviewer}, ISA Transactions.

		\item \textbf{Elsevier Reviewer}, Natural Language Processing Journal.

		\item \textbf{Elsevier Reviewer}, Journal of King Saud University - Computer
			and Information Sciences.

		\item \textbf{Reviewer}, 2022 4th International Conference on Deep Learning,
			Artificial Intelligence and Robotics (ICDLAIR2022).

		\item \textbf{Reviewer}, 2022 International Conference on Information Systems
			and Management Science (ISMS2022).

		\item \textbf{Reviewer}, 2022 International Conference on Communication and Information
			Systems (ICCIS2022).
	\end{itemize}

	\section{\textbf{Work Experiences}}

	\begin{joblong}
		{Software Engineer, REVE Systems Ltd.}{July 2023 - Present} \item Develop
		and implement scalable Java applications using advanced design patterns. \item
		Optimize data structures in Oracle DB for efficient storage and retrieval.
		\item Research and integrate new tools, libraries, APIs, and frameworks for enhanced
		performance.
	\end{joblong}

	\begin{joblong}
		{Software Engineer, BJIT Group}{April 2022 - June 2023} \item Implement
		JavaEE back-end/API using REST, SOAP, Spring, and microservices. \item Build
		enterprise apps using modern Java web frameworks and Thymeleaf. \item Create
		fundamental design documents, including API specifications and UMLs.
	\end{joblong}

	\begin{joblong}
		{Trainee Software Engineer, BJIT Group}{October 2021 - March 2022} \item
		Acquired foundational knowledge in software engineering through structured
		training. \item Assisted in coding, debugging, and testing while learning industry
		best practices. \item Developed skills in JavaEE, REST, SOAP, Spring, and
		front-end technologies.
	\end{joblong}

	\section{\textbf{Projects}}
	\begin{tabularx}
		{\linewidth}{ @{}l r@{} } \textbf{Customs Bond Management System, NBR} & \hfill
		\textit{\href{https://cusbond.gov.bd/}{Link to Demo}} \\[3.75pt]
		\multicolumn{2}{@{}X@{}}{%
		Responsibilities:
		\begin{itemize}[leftmargin=*]
			\item Held key roles across various modules of the CBMS project for the National
				Board of Revenue (NBR).

			\item Acted as the module owner including Legal and Case Information System,
				Utilization Declaration System.

			\item Implemented BGMEA and BKMEA Database integration for Utilization Declaration.

			\item Employed a diverse tech stack comprising Spring Boot, Thymeleaf, and
				Oracle DB for project execution.
		\end{itemize}
		}
		\\
	\end{tabularx}

	\begin{tabularx}
		{\linewidth}{ @{}l r@{} } \textbf{Rakuten Echiba Backend Development, Rakuten}
		& \hfill \textit{\href{https://www.rakuten.co.jp/}{Link to Demo}} \\[3.75pt]
		\multicolumn{2}{@{}X@{}}{%
		Responsibilities:
		\begin{itemize}[leftmargin=*]
			\item Solely focused on backend development for the Rakuten Echiba project
				utilizing Spring Boot framework.

			\item Managed Oracle database operations to ensure seamless data handling.

			\item Led the implementation of a custom framework tailored to meet project-specific
				requirements.
		\end{itemize}
		}
		\\
	\end{tabularx}

	\begin{tabularx}
		{\linewidth}{ @{}l r@{} } \textbf{Denka Pharmaceuticals Full-stack
		Development, Denka} & \hfill \textit{\href{https://www.denka.co.jp/eng/}{Link
		to Demo}} \\[3.75pt]
		\multicolumn{2}{@{}X@{}}{%
		Responsibilities:
		\begin{itemize}[leftmargin=*]
			\item Engaged in both backend and frontend development for Denka Pharmaceuticals.

			\item Utilized Spring Boot and Thymeleaf for backend and frontend development,
				respectively.

			\item Contributed to frontend enhancements using React JS.

			\item Managed data storage and retrieval using MySQL database.
		\end{itemize}
		}
		\\
	\end{tabularx}

	\begin{tabularx}
		{\linewidth}{ @{}l r@{} } \textbf{Mochida Pharmaceuticals Backend
		Development, Mochida} & \hfill \textit{\href{https://www.mochida.co.jp/english/}{Link
		to Demo}} \\[3.75pt]
		\multicolumn{2}{@{}X@{}}{%
		Responsibilities:
		\begin{itemize}[leftmargin=*]
			\item Developed backend functionalities for Mochida Pharmaceuticals using Spring
				Boot and Spring Batch.

			\item Implemented a unique database solution named Spiral DB to optimize data
				management processes.
		\end{itemize}
		}
		\\
	\end{tabularx}

	\section{\textbf{Skills}}
	\begin{tabularx}
		{\linewidth}{@{}l X@{}} \textbf{Core Skills} & \normalsize{OOP, REST API, SOAP, Micro-services, Data Structures, UML, Code Review}
		\\ \textbf{Programming Languages} & \normalsize{Java, JavaScript, Python} \\
		\textbf{Frameworks} & \normalsize{Spring Boot, Spring Batch, Bootstrap, Thymeleaf, React JS}
		\\ \textbf{Technical Tools} & \normalsize{Git, Postman, IntelliJ IDEA, DataGrip}
		\\ \textbf{Database Expertise} & \normalsize{Oracle, MySQL, MongoDB, Spiral DB}
		\\
	\end{tabularx}

	\section{\textbf{Extracurricular Activities}}

	\begin{itemize}[leftmargin=*,itemsep=2pt,parsep=0pt]
		\item \textbf{Guest Speaker}, entitled “How to get started: Undergraduate
			Research Journey”, organized by Computer \& Programming Club, Daffodil
			International University.

		\item \textbf{Vice President}, Research \& Career Wing (2021), Computer \&
			Programming Club, Daffodil International University.

		\item \textbf{Winner}, Data Science Hackathon – 2021 in Data Science Summit organized
			by Data Science Lab, Daffodil International University.

		\item \textbf{Session Instructor}, Workshop entitled “Python – Everything You
			Need to Know” organized by Computer \& Programming Club, Daffodil
			International University.

		\item \textbf{Speaker}, Webinar entitled “Session on Online Course” organized
			by Computer \& Programming Club, Daffodil International University.

		\item \textbf{Speaker}, Webinar entitled “Webinar on Research” organized by Some
			of Researchers in Daffodil International University.
	\end{itemize}

	\section{\textbf{References}}
	\begin{tabularx}
		{\linewidth}{@{}l X@{}}

		\textbf{Anisuzzaman Rubel} & Consultant \textendash Enterprise Integrator, Aspire
		to Innovate (a2i),
		\newline
		ICT Division, Dhaka, Bangladesh \\ & Contact: +880 1906-994487 \\ & Email: \href{mailto:anis.zaman@a2i.gov.bd}{anis.zaman@a2i.gov.bd}
		\\[3.75pt]

		\textbf{Md. Minhajur Rahman} & Senior General Manager, ENT\textendash4, Engineering
		Division,
		\newline
		BJIT Group, Dhaka, Bangladesh \\ & Contact: +880 1816-292692 \\ & Email: \href{mailto:minhajur.rahman@bjitgroup.com}{minhajur.rahman@bjitgroup.com}
		\\[3.75pt]
	\end{tabularx}

	\vfill
	\center{\footnotesize Updated On: \today}
\end{document}
