\section{\textbf{Leadership \& Team Management Experience}}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{Software Engineer L-II} & \hfill \textit{Akij iBOS Ltd.} \\[3.75pt]
    \multicolumn{2}{@{}X@{}}{%
        November 2024 – Present. \newline
        Responsibilities:
        \begin{itemize}[leftmargin=*]
            \item Led cross-functional development teams, coordinating backend, frontend, and QA units for enterprise projects.
            \item Defined development workflows and implemented agile delivery processes to ensure timely and efficient software releases.
            \item Mentored junior engineers, fostering a collaborative environment focused on clean code, design patterns, and technical excellence.
            \item Oversaw development of configurable rule-based systems to streamline business logic and decision automation.
            \item Improved deployment efficiency by over 40\% through CI/CD pipeline integration and automation strategies.
        \end{itemize}
    }
    \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{Vice President, Research \& Career Wing} & \hfill \textit{Career Pathway Club, Daffodil International University} \\[3.75pt]
    \multicolumn{2}{@{}X@{}}{%
        2021. \newline
        Responsibilities:
        \begin{itemize}[leftmargin=*]
            \item Directed student programs focusing on research exposure, career planning, and professional development.
            \item Organized seminars, tech talks, and interactive sessions with industry professionals and academic leaders.
            \item Advised undergraduate students on research methodology, academic publishing, and presentation skills.
        \end{itemize}
    }
    \\
\end{tabularx}
